Introducing Statistical Design of Experiments to SPARQL Endpoint Evaluation

### 2013-05-06 exp1/iswc2013.tex
explain implementation constraint
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@513 43ef1190-90fd-4dd7-a769-d0121f02b80e

\section{Experimens}

>>>>

\section{Experiments}

Common experiments include comparing several different
implementations. However, we focus on a slightly different problem: We
would like to compare the same implementation before and after some
change has been made, typically with the intention to enhance the
performance of the system. There are two reasons for this: One is that
there are currently many SPARQL implementations available, also Free
Software ones that can be modified by anyone, and the other is to
constrain the scope of the study to comparing two different things.
